Mechanical Detection of Dipole-Dipole Interactions \\between Electronic Spins in a Solid

### 2020-10-06 Mes papiers/Méca CR/Meca_cross_SI.tex
toto

>>>>

\subsection{$T_1$ Measurement}
%Include graphics...
The protocol to measure the spin lifetime of the NV centers is described in Fig. ... . The spins are initially polarized in their $m_s=\ket{0}$ state through a 1 ms green laser excitation pulse and then left to evolove in the dark for a variable dark time $\tau$. The spin state is finally read out with a 10 $\mu$s laser pulse, shorter than the polarization time of the spins.

The sequence is repeated a second time, adding a resonnant microwave $\pi$ pulse on a transition of one of the four classes of NV$^-$, exchanging the population of the $m_s=\ket{0}$ state with one of the $m_s=\ket{\pm 1}$ state.

The two sequences are then substracted, allowing us to measure the spin state population of a single class, and removing unwanted constributions such as charge state transfer in the dark.
